---
title: "Data Analysis Report with RMarkdown"
author: "Yuyan Zhang"
date: "2020/8/12"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---
```{r, include=FALSE}
# set work directory
# setwd('C:\\Users\\11623\\Documents\\GitHub\\bandit-task\\codes')

# import ----
library(tidyverse)
library(stringr)
library(lme4)
library(lmerTest)
library(ggplot2)
library(RColorBrewer)
library(effects)


# load data ----
rm(list = ls())
data1_models <- read.csv('data1_models.csv', header = F)
names(data1_models) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                         '2mid', '4mid', '8mid', '2high', '4high', '8high')
raw1 <- read.csv('data1_raw.csv', header = F)
raw1_trimmed <- raw1[, c(1:3, 5:13, 38)]
data1_models$age <- raw1[, 8]
data1_models$gender <- raw1[, 9]
data1_models$edu <- raw1[, 10]
data1_models$id <- 1:nrow(raw1)

# tidy
df1 <- data1_models %>% 
  pivot_longer(cols = 1:12, names_to = 'conditions',
               values_to = 'model') %>%
  mutate(num_arms = substr(conditions, 1, 1),
         demo = substr(conditions, 2, nchar(conditions)))
df1$id <- as.factor(df1$id)
df1$conditions <- factor(df1$conditions, 
                         levels = names(data1_models))
df1$model <- as.factor(df1$model)
levels(df1$model) <- c('Asocial RL', 'Random-choice', 
                       'Unconditional-copying',
                       'Copy-the-successful')
df1$num_arms <- as.factor(df1$num_arms)
df1$demo <- factor(df1$demo, levels = c('no', 'low', 'mid', 'high'))
levels(df1$demo) <- c('No', 'Bad', 'Medium', 'Good')
df1$demonstrator <- df1$demo
levels(df1$demonstrator) <- c('A. No Demonstrator', 
                              'B. "Bad" Demonstrator', 
                              'C. "Medium" Demonstrator', 
                              'D. "Good" Demonstrator')
df1 <- df1 %>% mutate(social = as.numeric(as.numeric(df1$model) >= 3))
df1$sum_rewards <- raw1[, 40] * 100 - 100

# add 'rewards'
data1_rewards <- raw1[, 39] %>% 
  as.character() %>%
  strsplit(',') %>%
  as.data.frame() %>%
  t() %>%
  as.data.frame()
names(data1_rewards) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                          '2mid', '4mid', '8mid', '2high', '4high', '8high')
names(data1_rewards) <- paste(names(data1_rewards), '_r', sep = '')
rownames(data1_rewards) <- c()
data1_rewards$id <- data1_models$id
df1_rewards <- data1_rewards %>%
  pivot_longer(1:12, names_to = 'conditions', values_to = 'sum_rewards')
df1_rewards$id <- as.factor(df1_rewards$id)
df1_rewards$conditions <- as.factor(df1_rewards$conditions)
df1_rewards$sum_rewards <- as.numeric(df1_rewards$sum_rewards)
df1$sum_rewards <- df1_rewards$sum_rewards

# data 2
data2_models <- read.csv('data2_models.csv', header = F)
names(data2_models) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                         '2mid', '4mid', '8mid', '2high', '4high', '8high')
raw2 <- read.csv('data2_raw.csv', header = F)
raw2_trimmed <- raw2[, c(1:3, 5:13, 38)]
data2_models$age <- raw2[, 8]
data2_models$gender <- raw2[, 9]
data2_models$edu <- raw2[, 10]
data2_models$id <- 1:nrow(raw2)

# tidy
df2 <- data2_models %>% 
  pivot_longer(cols = 1:12, names_to = 'conditions',
               values_to = 'model') %>%
  mutate(num_arms = substr(conditions, 1, 1),
         demo = substr(conditions, 2, nchar(conditions)))
df2$id <- as.factor(df2$id)
df2$conditions <- factor(df2$conditions, 
                         levels = names(data2_models))
df2$model <- as.factor(df2$model)
levels(df2$model) <- c('Asocial RL', 'Random-choice', 
                       'Unconditional-copying',
                       'Copy-the-successful')
df2$num_arms <- as.factor(df2$num_arms)
df2$demo <- factor(df2$demo, levels = c('no', 'low', 'mid', 'high'))
levels(df2$demo) <- c('No', 'Bad', 'Medium', 'Good')
df2$demonstrator <- df2$demo
levels(df2$demonstrator) <- c('A. No Demonstrator', 
                              'B. "Bad" Demonstrator', 
                              'C. "Medium" Demonstrator', 
                              'D. "Good" Demonstrator')
df2 <- df2 %>% mutate(social = as.numeric(as.numeric(df2$model) >= 3))
df2$sum_rewards <- raw2[, 40] * 100 - 100

# add 'rewards'
data2_rewards <- raw2[, 39] %>% 
  as.character() %>%
  strsplit(',') %>%
  as.data.frame() %>%
  t() %>%
  as.data.frame()
names(data2_rewards) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                          '2mid', '4mid', '8mid', '2high', '4high', '8high')
names(data2_rewards) <- paste(names(data2_rewards), '_r', sep = '')
rownames(data2_rewards) <- c()
data2_rewards$id <- data2_models$id
df2_rewards <- data2_rewards %>%
  pivot_longer(1:12, names_to = 'conditions', values_to = 'sum_rewards')
df2_rewards$id <- as.factor(df2_rewards$id)
df2_rewards$conditions <- as.factor(df2_rewards$conditions)
df2_rewards$sum_rewards <- as.numeric(df2_rewards$sum_rewards)
df2$sum_rewards <- df2_rewards$sum_rewards
```

# Demographic Statistics {.tabset .tabset-fade}
## Study 1
### Gender
```{r, echo=FALSE}
# descriptive statistics ----
# gender
tbl1_gender <- data1_models %>% 
  group_by(gender) %>%
  summarise(num_gender = n()) %>%
  as.data.frame()
knitr::kable(tbl1_gender)
```

### Age
```{r, echo=FALSE}
# age
tbl1_age <- data1_models %>%
  summarise(mean_age = mean(age),
            sd_age = sd(age),
            max_age = max(age),
            min_age = min(age)) %>%
  round(2)
knitr::kable(tbl1_age)
```

### Education Years

```{r, echo=FALSE}
# education year
tbl1_edu <- data1_models %>%
  summarise(mean_edu = mean(edu),
            sd_edu = sd(edu),
            max_edu = max(edu),
            min_edu = min(edu)) %>%
  round(2)
knitr::kable(tbl1_edu)
```

## Study 2

### Gender

```{r, echo=FALSE}
# data 2
# gender
tbl2_gender <- data2_models %>% 
  group_by(gender) %>%
  summarise(num_gender = n()) %>%
  as.data.frame()
knitr::kable(tbl2_gender)
```

### Age
```{r, echo=FALSE}
# age
tbl2_age <- data2_models %>%
  summarise(mean_age = mean(age),
            sd_age = sd(age),
            max_age = max(age),
            min_age = min(age)) %>%
  round(2)
knitr::kable(tbl2_age)
```

### Education Years
```{r, echo=FALSE}
# education year
tbl2_edu <- data2_models %>%
  summarise(mean_edu = mean(edu),
            sd_edu = sd(edu),
            max_edu = max(edu),
            min_edu = min(edu)) %>%
  round(2)
knitr::kable(tbl2_edu)
```


# Model Analysis {.tabset .tabset-fade}
## Study 1
### Number of Participants Using Each Model
```{r, echo=FALSE}
# models (descriptive table)
tbl1_mdl_full <- df1 %>% 
  group_by(conditions, model) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = model, values_from = n)
knitr::kable(tbl1_mdl_full)
```

### Number of Participants Using a Social or an Asocial Strategy
```{r, echo=FALSE}
tbl1_mdl_short <- df1 %>%
  group_by(conditions, social) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = social, values_from = n)
names(tbl1_mdl_short)[2:3] <- c('asocial', 'social')
knitr::kable(tbl1_mdl_short)

# always asocial / social
always1_aso <- df1 %>%
  group_by(id) %>%
  filter(sum(social) == 0) %>%
  select(id) %>%
  unique() %>%
  nrow()

always1_so <- df1 %>%
  group_by(id) %>%
  filter(sum(social) == 9) %>%
  select(id) %>%
  unique() %>%
  nrow()
```

There are `r always1_aso` participants always using an asocial strategy, and `r always1_so` participants always using a social one.

### Figure - Number of Participants Using Each Model

```{r, echo=FALSE}
# descriptive plot (output: 1350×350)
ggplot(data = df1, aes(x = num_arms, fill = model)) +
  geom_bar(position = 'stack') +
  xlab('Number of Arms') +
  ylab('Count of Participants') +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, nrow(data1_models) * 1.04)) +
  labs(fill = 'Models') + # legend title
  scale_fill_brewer(palette = 'RdBu', direction = -1) + # colours of bars
  facet_grid(~demonstrator) +
  theme_classic() +
  theme(text = element_text(family = 'serif'), # font setting
        axis.title = element_text(size = 18, face = 'bold'),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18, face = 'bold'),
        legend.text = element_text(size = 16),
        strip.text = element_text(size = 14, face = 'bold'), # facet title
        strip.background = element_rect(linetype = 0))
```

### The Effects of Arms Number and the Demonstrator's Performance on the Choice of a Social Strategy As Opposed to an Asocial One

```{r, echo=FALSE}
# model analysis ----
# MLR - asocial v.s. social
m1.main <- glmer(social ~ num_arms + demo + (1 | id),
                 data = filter(df1, demo != 'No'), family = 'binomial',
                 control = glmerControl(optimizer = 'bobyqa'))
summary(m1.main)
```

And the results can be illustrated as the figure below:

```{r, echo=FALSE}
# plot (800×500)
ggplot(data = filter(df1, demo != 'No'), 
       aes(x = num_arms, y = social, fill = demo)) +
  stat_summary(fun.data = mean_se, geom = 'bar',
               position = position_dodge(0.7), width = 0.7) +
  stat_summary(fun.data = mean_se, geom = 'errorbar', 
               position = position_dodge(0.7), width = 0.25) +
  xlab('Number of Arms') +
  ylab('Proportion of Using Social Strategies') +
  scale_y_continuous(expand = c(0, 0)) +
  labs(fill = 'Demonstrator', color = 'Demonstrator') +
  scale_fill_brewer(palette = 'BuGn') + 
  scale_color_brewer() +
  theme_classic() +
  theme(text = element_text(family = 'serif'), # font setting
        axis.title = element_text(size = 18, face = 'bold'),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18, face = 'bold'),
        legend.text = element_text(size = 16))

```


## Study 2
### Number of Participants Using Each Model
```{r, echo=FALSE}
# models (descriptive table)
tbl2_mdl_full <- df2 %>% 
  group_by(conditions, model) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = model, values_from = n)
knitr::kable(tbl2_mdl_full)
```

### Number of Participants Using a Social or an Asocial Strategy
```{r, echo=FALSE}
tbl2_mdl_short <- df2 %>%
  group_by(conditions, social) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = social, values_from = n)
names(tbl2_mdl_short)[2:3] <- c('asocial', 'social')
knitr::kable(tbl2_mdl_short)

# always asocial / social
always2_aso <- df2 %>%
  group_by(id) %>%
  filter(sum(social) == 0) %>%
  select(id) %>%
  unique() %>%
  nrow()

always2_so <- df2 %>%
  group_by(id) %>%
  filter(sum(social) == 9) %>%
  select(id) %>%
  unique() %>%
  nrow()
```

There are `r always2_aso` participants always using an asocial strategy, and `r always2_so` participants always using a social one.


### Figure - Number of Participants Using Each Model

```{r, echo=FALSE}
# descriptive plot (output: 1350×350)
ggplot(data = df2, aes(x = num_arms, fill = model)) +
  geom_bar(position = 'stack') +
  xlab('Number of Arms') +
  ylab('Count of Participants') +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, nrow(data2_models) * 1.04)) +
  labs(fill = 'Models') + # legend title
  scale_fill_brewer(palette = 'RdBu', direction = -1) + # colours of bars
  facet_grid(~demonstrator) +
  theme_classic() +
  theme(text = element_text(family = 'serif'), # font setting
        axis.title = element_text(size = 18, face = 'bold'),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18, face = 'bold'),
        legend.text = element_text(size = 16),
        strip.text = element_text(size = 14, face = 'bold'), # facet title
        strip.background = element_rect(linetype = 0))

```

### The Effects of Arms Number and the Demonstrator's Performance on the Choice of a Social Strategy As Opposed to an Asocial One

```{r, echo=FALSE}
# data 2
m2.main <- glmer(social ~ num_arms + demo + (1 | id),
                 data = filter(df2, demo != 'No'), family = 'binomial',
                 control = glmerControl(optimizer = 'bobyqa'))
summary(m2.main)
```

And the results can be illustrated as the figure below:

```{r, echo=FALSE}
# plot (800×500)
ggplot(data = filter(df2, demo != 'No'), 
       aes(x = num_arms, y = social, fill = demo)) +
  stat_summary(fun.data = mean_se, geom = 'bar',
               position = position_dodge(0.7), width = 0.7) +
  stat_summary(fun.data = mean_se, geom = 'errorbar', 
               position = position_dodge(0.7), width = 0.25) +
  xlab('Number of Arms') +
  ylab('Proportion of Using Social Strategies') +
  scale_y_continuous(expand = c(0, 0)) +
  labs(fill = 'Demonstrator', color = 'Demonstrator') +
  scale_fill_brewer(palette = 'BuGn') + 
  scale_color_brewer() +
  theme_classic() +
  theme(text = element_text(family = 'serif'), # font setting
        axis.title = element_text(size = 18, face = 'bold'),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18, face = 'bold'),
        legend.text = element_text(size = 16))
```


# Parameter Analysis {.tabset .tabset-fade}
```{r, echo=FALSE}
# load parameter data ----
# data 1
alpha <- read.csv('data1_paras_alpha.csv', header = F)
names(alpha) <- c('2', '4', '8')
alpha$id <- 1:50
paras1_alpha <- alpha %>% 
  pivot_longer(cols = 1:3, names_to = 'num_arms', values_to = 'alpha')
paras1_alpha$id <- as.factor(paras1_alpha$id)
paras1_alpha$num_arms <- as.factor(paras1_alpha$num_arms)

beta <- read.csv('data1_paras_beta.csv', header = F)
names(beta) <- c('2', '4', '8')
beta$id <- alpha$id
paras1_beta <- beta %>% 
  pivot_longer(cols = 1:3, names_to = 'num_arms', values_to = 'beta')
paras1_beta$id <- as.factor(paras1_beta$id)
paras1_beta$num_arms <- as.factor(paras1_beta$num_arms)

eta <- read.csv('data1_paras_eta.csv', header = F)
names(eta) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                '2mid', '4mid', '8mid', '2high', '4high', '8high')
eta$id <- alpha$id
paras1_eta <- eta %>% 
  select(4:13) %>%
  pivot_longer(cols = 1:9, names_to = 'conditions', values_to = 'eta')
paras1_eta$id <- as.factor(paras1_eta$id)
paras1_eta$num_arms <- paras1_eta$conditions %>% substr(1, 1)
paras1_eta$num_arms <- as.factor(paras1_eta$num_arms)
paras1_eta$demo <- paras1_eta$conditions %>% substr(2, 10)
paras1_eta$demo <- factor(paras1_eta$demo, 
                          levels = c('low', 'mid', 'high'))
levels(paras1_eta$demo) <- c('Bad', 'Medium', 'Good')

# data 2
alpha <- read.csv('data2_paras_alpha.csv', header = F)
names(alpha) <- c('2', '4', '8')
alpha$id <- 51:100
paras2_alpha <- alpha %>% 
  pivot_longer(cols = 1:3, names_to = 'num_arms', values_to = 'alpha')
paras2_alpha$id <- as.factor(paras2_alpha$id)
paras2_alpha$num_arms <- as.factor(paras2_alpha$num_arms)

beta <- read.csv('data2_paras_beta.csv', header = F)
names(beta) <- c('2', '4', '8')
beta$id <- alpha$id
paras2_beta <- beta %>% 
  pivot_longer(cols = 1:3, names_to = 'num_arms', values_to = 'beta')
paras2_beta$id <- as.factor(paras2_beta$id)
paras2_beta$num_arms <- as.factor(paras2_beta$num_arms)

eta <- read.csv('data2_paras_eta.csv', header = F)
names(eta) <- c('2no', '4no', '8no', '2low', '4low', '8low',
                '2mid', '4mid', '8mid', '2high', '4high', '8high')
eta$id <- alpha$id
paras2_eta <- eta %>% 
  select(4:13) %>%
  pivot_longer(cols = 1:9, names_to = 'conditions', values_to = 'eta')
paras2_eta$id <- as.factor(paras2_eta$id)
paras2_eta$num_arms <- paras2_eta$conditions %>% substr(1, 1)
paras2_eta$num_arms <- as.factor(paras2_eta$num_arms)
paras2_eta$demo <- paras2_eta$conditions %>% substr(2, 10)
paras2_eta$demo <- factor(paras2_eta$demo, 
                          levels = c('low', 'mid', 'high'))
levels(paras2_eta$demo) <- c('Bad', 'Medium', 'Good')

# take data1 & data2 together
paras1_alpha$show <- 'Hide'
paras1_beta$show <- 'Hide'
paras1_eta$show <- 'Hide'
paras2_alpha$show <- 'Show'
paras2_beta$show <- 'Show'
paras2_eta$show <- 'Show'

paras_alpha <- rbind(paras1_alpha, paras2_alpha)
paras_alpha$show <- factor(paras_alpha$show, 
                           levels = c('Hide', 'Show'))
paras_beta <- rbind(paras1_beta, paras2_beta)
paras_beta$show <- factor(paras_beta$show,
                          levels = c('Hide', 'Show'))
paras_eta <- rbind(paras1_eta, paras2_eta)
paras_eta$show <- factor(paras_eta$show, 
                         levels = c('Hide', 'Show'))

# combined df
df1$show <- 'Hide'
df2$show <- 'Show'
levels(df2$id) <- 51:100
df <- rbind(df1, df2)
df$show <- as.factor(df$show)

paras_alpha <- merge(paras_alpha, df %>% filter(demo == 'No'), 
                     by = c('id', 'num_arms', 'show'))
paras_beta <- merge(paras_beta, df %>% filter(demo == 'No'),
                    by = c('id', 'num_arms', 'show'))
paras_eta <- merge(paras_eta, df %>% filter(demo != 'No'), 
                   by = c('id', 'num_arms', 'demo', 'conditions', 'show'))

# combined paras
paras_all <- paras_alpha %>%
  select(id, num_arms, alpha) %>%
  merge(paras_beta) %>%
  select(id, num_arms, alpha, beta) %>%
  merge(paras_eta, by = c('id', 'num_arms'))
```

## Descriptive Statistics

alpha:


```{r, echo=FALSE}
# descriptive statistics ----
tbl_alpha <- paras_alpha %>% 
  group_by(show, num_arms) %>%
  summarise(m_alpha = mean(alpha) %>% round(2),
            sd_alpha = sd(alpha) %>% round(2))
knitr::kable(tbl_alpha)
```


beta:


```{r, echo=FALSE}
tbl_beta <- paras_beta %>% 
  group_by(show, num_arms) %>%
  summarise(m_beta = mean(beta) %>% round(2),
            sd_beta = sd(beta) %>% round(2))
knitr::kable(tbl_beta)
```

eta:

```{r, echo=FALSE}
tbl_eta <- paras_eta %>% 
  group_by(show, demo, num_arms) %>%
  summarise(m_eta = mean(eta) %>% round(2),
            sd_eta = sd(eta) %>% round(2)) 
knitr::kable(tbl_eta)
```

## Study 1
### The Effects of Arms Number and the Demonstrator's Performance on the Parameters


alpha:


```{r, echo=FALSE}
# parameter ~ num_arms + demo ----
# alpha
m1_alpha.null <- lmer(alpha ~ 1 + (1 | id), 
                      data = paras1_alpha, REML = F)
m1_alpha <- lmer(alpha ~ num_arms + (1 | id),
                 data = paras1_alpha, REML = F)
anova(m1_alpha.null, m1_alpha)
summary(m1_alpha)
```

beta:

```{r, echo=FALSE}
# beta
m1_beta.null <- lmer(log(beta) ~ 1 + (1 | id),
                     data = paras1_beta, REML = F)
m1_beta <- lmer(log(beta) ~ num_arms + (1 | id),
                data = paras1_beta, REML = F)
anova(m1_beta.null, m1_beta)
summary(m1_beta)
```

eta:

```{r, echo=FALSE}
# social
m1_eta.null <- lmer(eta ~ 1 + (1 | id),
                    data = paras1_eta,
                    REML = F)
m1_eta <- lmer(eta ~ num_arms + (1 | id),
               data = paras1_eta,
               REML = F)
m1_eta.0 <- lmer(eta ~ num_arms + demo + (1 | id),
                 data = paras1_eta,
                 REML = F)
m1_eta.1 <- lmer(eta ~ num_arms * demo + (1 | id),
                 data = paras1_eta,
                 REML = F)
anova(m1_eta.null, m1_eta, m1_eta.0, m1_eta.1)
summary(m1_eta.0)
```


## Study 2
### The Effects of Arms Number and the Demonstrator's Performance on the Parameters


alpha:


```{r, echo=FALSE}
m2_alpha.null <- lmer(alpha ~ 1 + (1 | id), 
                      data = paras2_alpha, REML = F)
m2_alpha <- lmer(alpha ~ num_arms + (1 | id),
                 data = paras2_alpha, REML = F)
anova(m2_alpha.null, m2_alpha)
summary(m2_alpha)
```


beta:


```{r, echo=FALSE}
m2_beta.null <- lmer(log(beta) ~ 1 + (1 | id),
                     data = paras2_beta, REML = F)
m2_beta <- lmer(log(beta) ~ num_arms + (1 | id),
                data = paras2_beta, REML = F)
anova(m2_beta.null, m2_beta)
summary(m2_beta)
```


eta:


```{r, echo=FALSE}
m2_eta.null <- lmer(eta ~ 1 + (1 | id),
                    data = paras2_eta,
                    REML = F)
m2_eta <- lmer(eta ~ num_arms + (1 | id),
               data = paras2_eta,
               REML = F)
m2_eta.0 <- lmer(eta ~ num_arms + demo + (1 | id),
                 data = paras2_eta,
                 REML = F)
m2_eta.1 <- lmer(eta ~ num_arms * demo + (1 | id),
                 data = paras2_eta,
                 REML = F)
anova(m2_eta.null, m2_eta, m2_eta.0, m2_eta.1)
summary(m2_eta.0)
```


## Taken Together
### The Effect of the Presence of the Demonstrator's Performance Level on the Parameters


alpha:


```{r, echo=FALSE}
# alpha - all insignificant
m_alpha.null <- lmer(alpha ~ 1 + (1 | id),
                     data = paras_alpha, REML = F)
m_alpha <- lmer(alpha ~ num_arms + (1 | id),
                data = paras_alpha, REML = F)
m_alpha.0 <- lmer(alpha ~ num_arms + show + (1 | id),
                  data = paras_alpha, REML = F)
m_alpha.1 <- lmer(alpha ~ num_arms * show + (1 | id),
                  data = paras_alpha, REML = F)
anova(m_alpha.null, m_alpha, m_alpha.0, m_alpha.1)
summary(m_alpha.1)
```


beta:


```{r, echo=FALSE}
# beta - only num_arms (m_beta) significant (same as before)
m_beta.null <- lmer(log(beta) ~ 1 + (1 | id),
                    data = paras_beta, REML = F)
m_beta <- lmer(log(beta) ~ num_arms + (1 | id),
               data = paras_beta, REML = F)
m_beta.0 <- lmer(log(beta) ~ num_arms + show + (1 | id),
                 data = paras_beta, REML = F)
m_beta.1 <- lmer(log(beta) ~ num_arms * show + (1 | id),
                 data = paras_beta, REML = F)
anova(m_beta.null, m_beta, m_beta.0, m_beta.1)
summary(m_beta)
```


eta:


```{r, echo=FALSE}
# eta (show insignificant)
m_eta.null <- lmer(eta ~ 1 + (1 | id),
                   data = paras_eta, REML = F)
m_eta <- lmer(eta ~ num_arms + (1 | id),
              data = paras_eta, REML = F)
m_eta.0 <- lmer(eta ~ num_arms + demo + (1 | id),
                data = paras_eta, REML = F)
m_eta.1 <- lmer(eta ~ num_arms + demo + show + (1 | id),
                data = paras_eta, REML = F)
m_eta.2 <- lmer(eta ~ num_arms + demo * show + (1| id),
                data = paras_eta, REML = F) # √
m_eta.3 <- lmer(eta ~ num_arms * demo * show + (1| id),
                data = paras_eta, REML = F)
anova(m_eta.null, m_eta, m_eta.0, m_eta.1, m_eta.2, m_eta.3)
summary(m_eta.2) # interaction significant!
```

### Figure - The Effect of the Presence of the Demonstrator's Performance Level on eta

```{r, echo=FALSE}
# figure (eta) (900×400)
ggplot(data = paras_eta, aes(x = num_arms, y = eta, fill = demo)) +
  stat_summary(fun.data = mean_se, geom = 'bar',
               position = position_dodge(0.7), width = 0.7) +
  stat_summary(fun.data = mean_se, geom = 'errorbar', 
               position = position_dodge(0.7), width = 0.25) +
  facet_grid(~show) +
  xlab('Number of Arms') +
  ylab('\U03B7') +
  scale_y_continuous(expand = c(0, 0)) +
  labs(fill = 'Demonstrator') +
  scale_fill_brewer(palette = 'BuGn') + 
  scale_color_brewer() +
  theme_classic() +
  theme(text = element_text(family = 'serif'), # font setting
        axis.title = element_text(size = 18, face = 'bold'),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18, face = 'bold'),
        legend.text = element_text(size = 16),
        strip.text = element_text(size = 16, face = 'bold'), # facet title
        strip.background = element_rect(linetype = 0))
```


# Individual Differences {.tabset .tabset-fade}
## Study 1
### The Effects of Demographic Features on the Parameters


alpha:


```{r, echo=FALSE}
# alpha
m1_idv_alpha.null <- lmer(alpha ~ 1 + (1 | id),
                          data = paras_alpha %>% filter(show == 'Hide'),
                          REML = F)
m1_idv_alpha <- lmer(alpha ~ age + edu + gender + (1 | id),
                    data = paras_alpha %>% filter(show == 'Hide'),
                    REML = F)
anova(m1_idv_alpha.null, m1_idv_alpha) # insignificant
summary(m1_idv_alpha) # insignificant 
```


beta:


```{r, echo=FALSE}
# beta
m1_idv_beta.null <- lmer(beta ~ 1 + (1 | id),
                         data = paras_beta %>% filter(show == 'Hide'),
                         REML = F)
m1_idv_beta <- lmer(beta ~ age + edu + gender + (1 | id),
                    data = paras_beta %>% filter(show == 'Hide'),
                    REML = F)
anova(m1_idv_beta.null, m1_idv_beta) # insignificant
summary(m1_idv_beta) # insignificant 
```


eta:


```{r, echo=FALSE}
# eta
m1_idv_eta.null <- lmer(eta ~ 1 + (1 | id),
                        data = paras_eta %>% filter(show == 'Hide'),
                        REML = F)
m1_idv_eta <- lmer(eta ~ edu + age + gender + (1 | id),
                   data = paras_eta %>% filter(show == 'Hide'),
                   REML = F)
anova(m1_idv_eta.null, m1_idv_eta) # insignificant
summary(m1_idv_eta) # gender significant
```


### The Effect of Asocial Exploration Tendency on Copying Rate


```{r, echo=FALSE}
m1_beta <- lmer(eta ~ num_arms + demo + (1 | id),
                data = paras_all %>% filter(show == 'Hide'), REML = F)
m1_beta.0 <- lmer(eta ~ num_arms + demo + beta + (1 | id),
                  data = paras_all %>% filter(show == 'Hide'), REML = F)
m1_beta.1 <- lmer(eta ~ (num_arms + demo) * beta + (1 | id),
                  data = paras_all %>% filter(show == 'Hide'), REML = F)
anova(m1_beta, m1_beta.0, m1_beta.1)
summary(m1_beta.0) # beta significant
```


## Study 2
### The Effects of Demographic Features on the Parameters


alpha:


```{r, echo=FALSE}
m2_idv_alpha.null <- lmer(alpha ~ 1 + (1 | id),
                          data = paras_alpha %>% filter(show == 'Show'),
                          REML = F)
m2_idv_alpha <- lmer(alpha ~ age + edu + gender + (1 | id),
                     data = paras_alpha %>% filter(show == 'Show'),
                     REML = F)
anova(m2_idv_alpha.null, m2_idv_alpha) # insignificant
summary(m2_idv_alpha) # insignificant
```


beta:


```{r, echo=FALSE}
m2_idv_beta.null <- lmer(beta ~ 1 + (1 | id),
                         data = paras_beta %>% filter(show == 'Show'),
                         REML = F)
m2_idv_beta <- lmer(beta ~ age + edu + gender + (1 | id),
                    data = paras_beta %>% filter(show == 'Show'),
                    REML = F)
anova(m2_idv_beta.null, m2_idv_beta) # insignificant
summary(m2_idv_beta) # gender significant 
```


eta:


```{r, echo=FALSE}
m2_idv_eta.null <- lmer(eta ~ 1 + (1 | id),
                        data = paras_eta %>% filter(show == 'Show'),
                        REML = F)
m2_idv_eta <- lmer(eta ~ edu + age + gender + (1 | id),
                   data = paras_eta %>% filter(show == 'Show'),
                   REML = F)
anova(m2_idv_eta.null, m2_idv_eta) # insignificant
summary(m2_idv_eta) # insignificant
```


### The Effect of Asocial Exploration Tendency on Copying Rate


```{r, echo=FALSE}
m2_beta <- lmer(eta ~ num_arms + demo + (1 | id),
                data = paras_all %>% filter(show == 'Show'), REML = F)
m2_beta.0 <- lmer(eta ~ num_arms + demo + beta + (1 | id),
                  data = paras_all %>% filter(show == 'Show'), REML = F)
m2_beta.1 <- lmer(eta ~ (num_arms + demo) * beta + (1 | id),
                  data = paras_all %>% filter(show == 'Show'), REML = F)
anova(m2_beta, m2_beta.0, m2_beta.1) # insignificant
summary(m2_beta.0) # beta insignificant
```
